Comparison between both and none categories

### 2022-09-21 analysis/both_none.Rmd
upload analysis to compare both and none categories
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Comparison between baseline and test performance'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of primary analysis.

@@

```{r file, include = FALSE}
data_ioi = "preprosessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprosessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprosessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprosessor/trimmed/dt_vel_diff_trimmed.txt"
data_baseline_ioi = "preprosessor/predata/trimmed/dt_ioi_trimmed.txt"
data_baseline_kot = "preprosessor/predata/trimmed/dt_kot_trimmed.txt"
data_baseline_vel = "preprosessor/predata/trimmed/dt_vel_trimmed.txt"
data_baseline_vel_diff = "preprosessor/predata/trimmed/dt_vel_diff_trimmed.txt"
```

@@

```{r, include = FALSE}
# combine data with baseline performance
dt_bl_ioi <- fread(data_baseline_ioi, header = T, sep = ",", dec = ".")
dt_bl_kot <- fread(data_baseline_kot, header = T, sep = ",", dec = ".")
dt_bl_vel <- fread(data_baseline_vel, header = T, sep = ",", dec = ".")
dt_bl_vel_diff <- fread(data_baseline_vel_diff, header = T, sep = ",", dec = ".")

dt_bl_ioi$Articulation <- "Baseline"
dt_bl_kot$Articulation <- "Baseline"
dt_bl_vel$Articulation <- "Baseline"
dt_bl_vel_diff$Articulation <- "Baseline"

dt_bl_ioi$Dynamics <- "Baseline"
dt_bl_kot$Dynamics <- "Baseline"
dt_bl_vel$Dynamics <- "Baseline"
dt_bl_vel_diff$Dynamics <- "Baseline"

dt_bl_ioi$Category <- "baseline"
dt_bl_kot$Category <- "baseline"
dt_bl_vel$Category <- "baseline"
dt_bl_vel_diff$Category <- "baseline"

dt_ioi <- rbind(dt_ioi, dt_bl_ioi)
dt_kot <- rbind(dt_kot, dt_bl_kot)
dt_vel <- rbind(dt_vel, dt_bl_vel)
dt_vel_diff <- rbind(dt_vel_diff, dt_bl_vel_diff)
```

# IOI 
## 1. Individual
```{r ioi}
# for each individual
ioi_trial <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category)]

@@

```{r seq-ioi, fig.width = 7, fig.height = 2}
ioi_seq <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Category, Interval)]

@@

```{r}
aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

@@

```{r kot, echo = FALSE}
# for each individual
kot_trial <- dt_kot[Subcomponent1 == "Legato" | Subcomponent1 == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent1)]

@@

```{r seq-kot, fig.width = 7, fig.height = 2}
kot_seq <- dt_kot[, .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Category, Interval)]

@@

```{r vel, echo = FALSE}
# for each individual
vel_trial <- dt_vel[Subcomponent2 != "NA", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r seq-vel, fig.width = 7, fig.height = 2}
vel_seq <- dt_vel[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Category, RowNr)]

@@

```{r vel-diff, echo = FALSE}
# for each individual
vel_diff_trial <- dt_vel_diff[Subcomponent2 == "FtoP" | Subcomponent2 == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r seq-vel-diff, fig.width = 7, fig.height = 2}
vel_diff_seq <- dt_vel_diff[, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Category, Interval)]

>>>>

---
title: 'Comparison between both and none categories'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of analysis comparing between both and none categories.

@@

```{r file, include = FALSE}
data_ioi = "preprosessor/trimmed/dt_ioi_trimmed.txt"
data_kot = "preprosessor/trimmed/dt_kot_trimmed.txt"
data_vel = "preprosessor/trimmed/dt_vel_trimmed.txt"
data_vel_diff = "preprosessor/trimmed/dt_vel_diff_trimmed.txt"
```

@@

# IOI 
## 1. Individual
```{r ioi}
# for each individual
ioi_trial <- dt_ioi[Category == "none" | Category == "both", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category)]

@@

```{r seq-ioi, fig.width = 7, fig.height = 2}
ioi_seq <- dt_ioi[Category == "none" | Category == "both", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Category, Interval)]

@@

```{r}
aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

```

@@

```{r kot, echo = FALSE}
# for each individual
dt_subset_kot <- dt_kot[Subcomponent1 == "Legato" | Subcomponent1 == "Staccato"]
kot_trial <- dt_subset_kot[Category == "none" | Category == "both", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent1)]

@@

```{r seq-kot, fig.width = 7, fig.height = 2}
kot_seq <- dt_kot[Category == "none" | Category == "both", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Category, Interval)]

@@

```{r vel, echo = FALSE}
# for each individual
dt_subset_vel <- dt_vel[Subcomponent2 != "NA"]
vel_trial <- dt_subset_vel[Category == "none" | Category == "both", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r seq-vel, fig.width = 7, fig.height = 2}
vel_seq <- dt_vel[Category == "none" | Category == "both", .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Category, RowNr)]

@@

```{r vel-diff, echo = FALSE}
# for each individual
dt_subset_vel_diff <- dt_vel_diff[Subcomponent2 == "FtoP" | Subcomponent2 == "PtoF"]
vel_diff_trial <- dt_subset_vel_diff[Category == "none" | Category == "both", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, TrialNr, Stimuli, Articulation, Dynamics, Category, Subcomponent2)]

@@

```{r seq-vel-diff, fig.width = 7, fig.height = 2}
vel_diff_seq <- dt_vel_diff[Category == "none" | Category == "both", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Category, Interval)]
